---
title: "PK Example (Theophylline)"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r}
library(tidyverse)
library(mlxR)

theme_set(theme_bw(base_size=14))
```


## Simulate a trial using the original design

[PK example link](http://simulx.webpopix.org/case-studies/workflow-pk1/)

```{r}
project.file <- 'monolixRuns/theophylline_project.mlxtran'
sim.res1 <- simulx(project = project.file)

#sim.res1
```

sim.res1 contains 4 list.   

* list1 ; y1 ; observed data
* iist2 ; treatment ; dosing data
* list3 ; originalId 
* list4 ; population ; population parameters


```{r}
ggplot(data = sim.res1$y1, aes(time, y1, colour=id))+
  geom_point()+
  geom_line()+
  scale_x_continuous("Time") + scale_y_continuous("Concentration")

```

## Remove the residual error

1) First, parameter `b` was set as 0.  
2) Add individual predicted value `Cc` in the simulated result.  
3) Simulation using updated output and parameters


```{r}
sim.param <- c(b=0)
out <- list(name = 'Cc', time = seq(0, 25, by=0.1))
sim.res2 <- simulx(project = project.file,
                   output = out,
                   parameter = sim.param)

ggplot()+
  geom_point(data = sim.res2$y1, aes(time, y1, colour=id))+
  geom_line(data = sim.res2$Cc, aes(time, Cc, colour=id))+
  scale_x_continuous("Time") + scale_y_continuous("Concentration")

#sim.res2
```

## Simulate a trial with N individuals

If we want to simulate more subjects using same population parameters?

```{r}
n_sim <- 50

sim.res3 <- simulx(project = project.file,
                   group = list(size = n_sim))

ggplot()+
  geom_point(data = sim.res3$y1, aes(time, y1, colour=id))+
  geom_line(data = sim.res3$y1, aes(time, y1, colour=id))+
  scale_x_continuous("Time") + scale_y_continuous("Concentration")+
  theme(legend.position = 'none')

```
```{r}
n_sim <- 3

out  <- list(name = 'Cc', time = seq(0, 25, by=0.1))
sim.res3 <- simulx(project = project.file,
                   output = out,
                   group = list(size = n_sim))

ggplot()+
  geom_point(data = sim.res3$y1, aes(time, y1, colour=id))+
  geom_line(data = sim.res3$Cc, aes(time, Cc, colour=id))+
  scale_x_continuous("Time") + scale_y_continuous("Concentration")+
  theme(legend.position = 'none')
```
## Define new observation times

```{r}
out  <- list(name = 'y1', time = (0:12))

sim.res4  <- simulx(project = project.file,
                    output = out)

print(ggplot(data=sim.res4$y1) + 
        geom_point(aes(x=time, y=y1, colour=id)) +
        geom_line(aes(x=time, y=y1, colour=id)) +
        scale_x_continuous("Time") + scale_y_continuous("Concentration"))
```
```{r}
#sim.res4
```

## Output the predicted concentrations, the individual parameters and the covariates

```{r}
out1  <- list(name = 'y1', time = seq(0, 24, by=2))
out2  <- list(name = 'Cc', time = seq(0, 24, by=0.1))
out3  <- list(name = c('V', 'Cl', 'WEIGHT'))

sim.res5  <- simulx(project = project.file,
                    output  = list(out1, out2, out3))

print(sim.res5$parameter)

#sim.res5
```
```{r}
print(ggplot() + 
        geom_point(data=sim.res5$y1,aes(x=time, y=y1, colour=id)) +
        geom_line(data=sim.res5$Cc,aes(x=time, y=Cc, colour=id)) +
        scale_x_continuous("Time") + scale_y_continuous("Concentration"))
```

## Specify the administration schedule

```{r}
adm   <- list(time = c(0,6), amount = c(320, 320))

sim.res6  <- simulx(project   = project.file,
                    treatment = adm,
                    output    = list(out1, out2))

print(ggplot() + 
        geom_point(data=sim.res6$y1,aes(x=time, y=y1, colour=id)) +
        geom_line(data=sim.res6$Cc,aes(x=time, y=Cc, colour=id)) +
        scale_x_continuous("Time") + scale_y_continuous("Concentration"))
```

## pecify own WEIGHT covariates for N patients
```{r}
N       <- 100
weight <- list( name     = 'WEIGHT', 
                colNames = c('id', 'WEIGHT'),
                value    = cbind(c(1:N),c(rep(50, N/2), rep(90, N/2))))

adm   <- list(time = 0, amount = 500)

sim.res7 <- simulx(project = project.file, 
                   output = list(out1, out2),
                   treatment = adm,
                   parameter = weight)

sim.res7$Cc$weight <- 50
sim.res7$Cc$weight[as.numeric(sim.res7$Cc$id)>N/2] <-90
sim.res7$Cc$weight <- as.factor(sim.res7$Cc$weight)

print(ggplot() + 
        geom_line(data=sim.res7$Cc,aes(x=time, y=Cc, group=id, colour=weight)) +
        scale_x_continuous("Time") + scale_y_continuous("Concentration"))
```


